### 2019-02-19 2-Chapters/5-Chapter/ALT_2018__MPBandits.git/mpBandits.tex
Small modifications today. Hard to get anything important done, I had a review to do for a COLT paper...

% -----------------------------------------------------------------
\section{Multi-Player Bandit Model with Different Feedback Levels}
\label{sec:5:model}
% -----------------------------------------------------------------

@@

% -----------------------------------------------------------------
\section{An Asymptotic Regret Lower Bound for a certain class of algorithms}
\label{sec:5:lowerbound}
% -----------------------------------------------------------------

@@

% -----------------------------------------------------------------
\subsection{A Useful Regret Decomposition}
\label{sub:5:defregret}

@@

% -----------------------------------------------------------------
\subsection{An Improved Asymptotic Lower Bound on the Regret}
\label{sub:5:betterLowerBound}

@@

% -----------------------------------------------------------------
\subsection{Towards Regret Upper Bounds}

@@

% -----------------------------------------------------------------
\section{New Algorithms for Multi-Player Bandits}
\label{sec:5:algorithms}
% -----------------------------------------------------------------

@@

\subsection{Two New Strategies Based on Indices and Orthogonalization: \RandTopM{} and \MCTopM}
\label{sub:5:RandTopM_and_MCTopM}

@@

% -----------------------------------------------------------------
\subsection{The \Selfish{} Approach}
\label{sub:5:Selfish}

@@

% -----------------------------------------------------------------
\section{Empirical performances}
\label{sec:5:experiments}
% -----------------------------------------------------------------

@@

% -----------------------------------------------------------------
\subsection{Common Analysis for \RandTopM- and \MCTopM-\klUCB{}}\label{sub:5:UpperBoundSelections}

@@

% -----------------------------------------------------------------
\subsection{Regret Analysis of \MCTopM-\klUCB}\label{sub:5:UpperBoundCollisions}

>>>>

% -----------------------------------------------------------------
\section{Multi-player bandit model with different feedback levels}
\label{sec:5:model}
% -----------------------------------------------------------------

@@

% -----------------------------------------------------------------
\section{An improved asymptotic regret lower bound for a certain class of algorithms}
\label{sec:5:lowerbound}
% -----------------------------------------------------------------

@@

% -----------------------------------------------------------------
\subsection{A useful regret decomposition}
\label{sub:5:defregret}

@@

% -----------------------------------------------------------------
\subsection{An improved asymptotic lower bound on the regret}
\label{sub:5:betterLowerBound}

@@

% -----------------------------------------------------------------
\subsection{Towards regret upper bounds}

@@

% -----------------------------------------------------------------
\section{New algorithms for multi-player bandits}
\label{sec:5:algorithms}
% -----------------------------------------------------------------

@@

\subsection{Two new strategies based on indices and orthogonalization: \RandTopM{} and \MCTopM}
\label{sub:5:RandTopM_and_MCTopM}

@@

% -----------------------------------------------------------------
\subsection{The \Selfish{} approach}
\label{sub:5:Selfish}

@@

% -----------------------------------------------------------------
\section{Numerical simulations}
\label{sec:5:experiments}
% -----------------------------------------------------------------

@@

% -----------------------------------------------------------------
\subsection{Common analysis for \RandTopM- and \MCTopM-\klUCB{}}\label{sub:5:UpperBoundSelections}

@@

% -----------------------------------------------------------------
\subsection{Regret analysis of \MCTopM-\klUCB}\label{sub:5:UpperBoundCollisions}

### 2019-02-19 2-Chapters/6-Chapter/nonstatbandits.git/NonStatB.tex
Small modifications today. Hard to get anything important done, I had a review to do for a COLT paper...

We report results obtained on three different piece-wise stationary bandit problems, illustrated in Figure~\ref{fig:6:Problems_123} in Appendix~\ref{app:6:Figures}, and described in more details below. Additional results on two more problems can be found in Appendix~\ref{sub:6:TwoMoreProblems}, where additional regret curves can be found for all problems. For each experiment, the regret was estimated using $1000$ independent runs.

>>>>

We report results obtained on three different piece-wise stationary bandit problems, illustrated in Figures~\ref{fig:6:Problem_1}, \ref{fig:6:Problem_2} and \ref{fig:6:Problem_5} in Appendix~\ref{app:6:Figures}, and described in more details below. Additional results on two more problems can be found in Appendix~\ref{sub:6:TwoMoreProblems}, where additional regret curves can be found for all problems. For each experiment, the regret was estimated using $1000$ independent runs.
